---
title: 'visualization mid #1'
author: "Yuru Li"
date: "10/21/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# install packages
```{r}
library(ggplot2)
library(stringr)
library(dplyr)
library(gridExtra)
library(lubridate)
library(broom)
```

# import dataset + convert all letter to lower case
```{r}
market <- read.csv("/Users/yuru/Documents/IE 6600 SEC03 18025 Computation and Visualization for Analytics/midterm#1/farmers_market_info.csv",sep = ",",header = T)
market <- as.data.frame(sapply(market, tolower))


```

# Problem 1
gives geography based insights about the farmers market.

Group the different states
```{r}
# Defined by United States Census Bureau
Northeast <- tolower(c('Connecticut', 'Maine', 'Massachusetts', 'New Hampshire', 'Rhode Island',  'Vermont','New Jersey', 'New York', 'Pennsylvania'))

Midwest <- tolower(c('Illinois', 'Indiana', 'Michigan', 'Ohio', 'Wisconsin','Iowa', 'Kansas', 'Minnesota', 'Missouri', 'Nebraska', 'North Dakota', 'South Dakota'))

South <- tolower(c('Delaware', 'Florida', 'Georgia', 'Maryland', 'North Carolina', 'South Carolina', 'Virginia', 'Washington D.C.', 'West Virginia','Alabama', 'Kentucky', 'Mississippi', 'Tennessee','Arkansas', 'Louisiana', 'Oklahoma', 'Texas'))

West <- tolower(c('Arizona', 'Colorado', 'Idaho', 'Montana', 'Nevada', 'New Mexico', 'Utah', 'Wyoming','Alaska', 'California', 'Hawaii', 'Oregon', 'Washington'))
```

Trim whitespace
```{r}
market$State <- str_trim(market$State, "both")
market$County <- str_trim(market$County, "both")
market$city <- str_trim(market$city, "both")
```

Subsetting dataset
```{r}
market_sub_Northeast <- subset(market, State %in% Northeast)
market_sub_Midwest <- subset(market, State %in% Midwest)
market_sub_South <- subset(market, State %in% South)
market_sub_West <- subset(market, State %in% West)
```

Summarise info
```{r}
market_Northeast <- summarise(group_by(market_sub_Northeast,State),count=n())
market_Midwest <- summarise(group_by(market_sub_Midwest,State),count=n())
market_South <- summarise(group_by(market_sub_South,State),count=n())
market_West <- summarise(group_by(market_sub_West,State),count=n())

```

```{r}
market_Northeast_area <- market_Northeast
market_Midwest_area <- market_Midwest
market_South_area <- market_South
market_West_area <- market_West

market_Northeast_area$area <- "Northeast"
market_Midwest_area$area <- "Midwest"
market_South_area$area <- "South"
market_West_area$area <- "West"
```

```{r}
market_areas_bind <- rbind(market_Northeast_area,market_Midwest_area,market_South_area,market_West_area)
market_areas_bind
```

```{r fig.height=7, fig.width=7}
ggplot(market_areas_bind,aes(reorder(State,count),count,fill=area))+
  geom_bar(stat="identity")+
  coord_flip()+
  ggtitle("Farmers Market Distribution over US")+
  xlab("State")+
  ylab("Number of Farmers Market")+
  labs(fill="US Area")+
  theme(axis.text.y = element_text(color = "grey20", size = 13),
        axis.text.x = element_text(color = "grey20", size = 13),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold")
        )+
  geom_hline(aes(yintercept=mean(count)),color="blue")+
  scale_fill_manual(values = c("#44bec7","#ffc300","#fa3c4c","#d696bb"))
  
```




Plot (abandoned plot, keep for personel record)
```{r fig.height=6, fig.width=6}

plot_market_Northeast <- ggplot(market_Northeast,aes(x=reorder(State,count),y=count))+
  geom_bar(stat = "identity",fill="#007777")+
  coord_flip()+
  xlab("States in Northeast US")+
  ylab("Number of Farmers Market")+
  ggtitle("Northeast US")+ 
  theme(axis.text.y = element_text(color = "grey20", size = 13),
        axis.text.x = element_text(color = "grey20", size = 13),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold")
        )+
  geom_text(aes(label = count), nudge_y = 30, color = "yellow4",size=5)+
  ylim(0, 800)

plot_market_Midwest <- ggplot(market_Midwest,aes(x=reorder(State,count),y=count))+
  geom_bar(stat = "identity",fill="#007777")+
  coord_flip()+
  xlab("States in Midwest US")+
  ylab("Number of Farmers Market")+
  ggtitle("Midwest US")+ 
  theme(axis.text.y = element_text(color = "grey20", size = 13),
        axis.text.x = element_text(color = "grey20", size = 13),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold")
        )+
  geom_text(aes(label = count), nudge_y = 30, color = "yellow4",size=5)+
  ylim(0, 800)

plot_market_South <- ggplot(market_South,aes(x=reorder(State,count),y=count))+
  geom_bar(stat = "identity",fill="#007777")+
  coord_flip()+
  xlab("States in South US")+
  ylab("Number of Farmers Market")+
  ggtitle("South US")+ 
  theme(axis.text.y = element_text(color = "grey20", size = 13),
        axis.text.x = element_text(color = "grey20", size = 13),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold")
        )+
  geom_text(aes(label = count), nudge_y = 30, color = "yellow4",size=5)+
  ylim(0, 800)

plot_market_West <- ggplot(market_West,aes(x=reorder(State,count),y=count))+
  geom_bar(stat = "identity",fill="#007777")+
  coord_flip()+
  xlab("States in West US")+
  ylab("Number of Farmers Market")+
  ggtitle("West US")+ 
  geom_text(aes(label = count), nudge_y = 30, color = "yellow4",size=5)+
  theme(axis.text.y = element_text(color = "grey20", size = 13),
        axis.text.x = element_text(color = "grey20", size = 13),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold")
        )+
  ylim(0, 800)

grid.arrange(plot_market_Northeast, plot_market_Midwest, plot_market_South,plot_market_West,ncol = 2)
```




# Problem 2
```{r}
#dates <- as.Date(market[1,13], "%m/%d/%Y")
#dates
#dates <- as.Date(market[1,13], "%m/%d/%Y to %m/%d/%Y")
#dates
#,15,17,19
market_sub_time_1 <- as.data.frame(market[,c(1,13)])
market_sub_time_1
dates_1_1 <- as.Date(market_sub_time_1[1,2], "%m/%d/%Y")
dates_1_1
dates_1_2 <- as.Date(market_sub_time_1[1,2], "%m/%d/%Y to %m/%d/%Y")
dates_1_2

#Season1
dates_S1_D1 <- c()
dates_S1_D2 <- c()
for( i in 1:nrow(market_sub_time_1) ){
  dates_S1_D1 <- append(dates_S1_D1,as.Date(market_sub_time_1[i,2], "%m/%d/%Y"))
  dates_S1_D2 <- append(dates_S1_D2,as.Date(market_sub_time_1[i,2], "%m/%d/%Y to %m/%d/%Y"))
}
FMID_1 <- as.data.frame(market_sub_time_1[,1])
dates_S1_D1 <- as.data.frame(dates_S1_D1)
dates_S1_D2 <- as.data.frame(dates_S1_D2)

market_time_S1<- na.omit(cbind(FMID_1,dates_S1_D1,dates_S1_D2))
market_time_S1

```

```{r}
Season1_year <- factor(year(market_time_S1$dates_S1_D1))
Season1_year <- as.data.frame(tidy(summary(Season1_year)))


colnames(Season1_year) <- c("year","count")
Season1_year
```

```{r}
#Season2
market_sub_time_2 <- as.data.frame(market[,c(1,15)])

dates_S2_D1 <- c()
dates_S2_D2 <- c()
for( i in 1:nrow(market_sub_time_2) ){
  dates_S2_D1 <- append(dates_S2_D1,as.Date(market_sub_time_2[i,2], "%m/%d/%Y"))
  dates_S2_D2 <- append(dates_S2_D2,as.Date(market_sub_time_2[i,2], "%m/%d/%Y to %m/%d/%Y"))
}
FMID_2 <- as.data.frame(market_sub_time_2[,1])
dates_S2_D1 <- as.data.frame(dates_S2_D1)
dates_S2_D2 <- as.data.frame(dates_S2_D2)

market_time_S2<- na.omit(cbind(FMID_2,dates_S2_D1,dates_S2_D2))
market_time_S2

Season2_year <- factor(year(market_time_S2$dates_S2_D1))
Season2_year <- as.data.frame(tidy(summary(Season2_year)))


colnames(Season2_year) <- c("year","count")
Season2_year
```

```{r}
#Season3
market_sub_time_3 <- as.data.frame(market[,c(1,17)])

dates_S3_D1 <- c()
dates_S3_D2 <- c()
for( i in 1:nrow(market_sub_time_3) ){
  dates_S3_D1 <- append(dates_S3_D1,as.Date(market_sub_time_3[i,2], "%m/%d/%Y"))
  dates_S3_D2 <- append(dates_S3_D2,as.Date(market_sub_time_3[i,2], "%m/%d/%Y to %m/%d/%Y"))
}
FMID_3 <- as.data.frame(market_sub_time_3[,1])
dates_S3_D1 <- as.data.frame(dates_S3_D1)
dates_S3_D2 <- as.data.frame(dates_S3_D2)

market_time_S3<- na.omit(cbind(FMID_3,dates_S3_D1,dates_S3_D2))
market_time_S3

Season3_year <- factor(year(market_time_S3$dates_S3_D1))
Season3_year <- as.data.frame(tidy(summary(Season3_year)))


colnames(Season3_year) <- c("year","count")
Season3_year
```

```{r}
#Season4
market_sub_time_4 <- as.data.frame(market[,c(1,19)])

dates_S4_D1 <- c()
dates_S4_D2 <- c()
for( i in 1:nrow(market_sub_time_4) ){
  dates_S4_D1 <- append(dates_S4_D1,as.Date(market_sub_time_4[i,2], "%m/%d/%Y"))
  dates_S4_D2 <- append(dates_S4_D2,as.Date(market_sub_time_4[i,2], "%m/%d/%Y to %m/%d/%Y"))
}
FMID_4 <- as.data.frame(market_sub_time_4[,1])
dates_S4_D1 <- as.data.frame(dates_S4_D1)
dates_S4_D2 <- as.data.frame(dates_S4_D2)

market_time_S4<- na.omit(cbind(FMID_4,dates_S4_D1,dates_S4_D2))
market_time_S4

Season4_year <- factor(year(market_time_S4$dates_S4_D1))
Season4_year <- as.data.frame(tidy(summary(Season4_year)))


colnames(Season4_year) <- c("year","count")
Season4_year
```

```{r}
#Join 4 tables together
join_4_Season<- full_join(full_join(full_join(Season1_year,Season2_year,by=c("year"="year")),Season3_year,by=c("year"="year")),Season4_year,by=c("year"="year"))
join_4_Season[is.na(join_4_Season)] <- 0

join_4_Season$count <- join_4_Season$count.x+join_4_Season$count.y+join_4_Season$count.x.x+join_4_Season$count.y.y

join_4_Season <- join_4_Season[1:(nrow(join_4_Season)-1),c(1,6)]
join_4_Season
```

```{r}
ggplot(join_4_Season,aes(factor(year),count,group=1))+
  geom_line()+
  geom_point()+
  ggtitle("The Trend of Farmer Market Attendance")+
  xlab("Year")+
  ylab("Count")+  
  theme(axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold")
        )
```


# Problem 3
*Give product based insights that helps the client to understand the type of products or product mix in farmers market across the country*

Trim whitespace
```{r}
truth <- sapply(market,is.character)
market <- data.frame(cbind(sapply(market[,truth],trimws,which="both"),market[,!truth]))
```

market_sub_Northeast 
market_sub_Midwest
market_sub_South
market_sub_West 
```{r}
#market_sub_Northeast 

N_yes_count <- c()
for(i in 29:54){
  N_yes_count <- append(N_yes_count,
                      as.numeric(as.data.frame(table(market_sub_Northeast[,i]))[which(as.data.frame(table(market_sub_Northeast[,i]))$Var1=='y'),2]))
}

N_no_count <- c()
for(i in 29:54){
  N_no_count <- append(N_no_count,
                      as.numeric(as.data.frame(table(market_sub_Northeast[,i]))[which(as.data.frame(table(market_sub_Northeast[,i]))$Var1=='n'),2]))
}

N_column_name <- colnames(market_sub_Northeast[,29:54])



N_T_3_1 <- cbind(as.data.frame(N_column_name),YorN='y',as.data.frame(N_yes_count))
colnames(N_T_3_1)[3] <- 'count'

N_T_3_2 <- cbind(as.data.frame(N_column_name),YorN='n',as.data.frame(N_no_count))
colnames(N_T_3_2)[3] <- 'count'

N_T_3 <- rbind(N_T_3_1,N_T_3_2)
N_T_3

```

```{r}
#market_sub_Midwest
M_yes_count <- c()
for(i in 29:54){
  M_yes_count <- append(M_yes_count,
                      as.numeric(as.data.frame(table(market_sub_Midwest[,i]))[which(as.data.frame(table(market_sub_Midwest[,i]))$Var1=='y'),2]))
}

M_no_count <- c()
for(i in 29:54){
  M_no_count <- append(M_no_count,
                      as.numeric(as.data.frame(table(market_sub_Midwest[,i]))[which(as.data.frame(table(market_sub_Midwest[,i]))$Var1=='n'),2]))
}

M_column_name <- colnames(market_sub_Midwest[,29:54])



M_T_3_1 <- cbind(as.data.frame(M_column_name),YorN='y',as.data.frame(M_yes_count))
colnames(M_T_3_1)[3] <- 'count'

M_T_3_2 <- cbind(as.data.frame(M_column_name),YorN='n',as.data.frame(M_no_count))
colnames(M_T_3_2)[3] <- 'count'

M_T_3 <- rbind(M_T_3_1,M_T_3_2)
M_T_3
```

```{r}
#market_sub_South
S_yes_count <- c()
for(i in 29:54){
  S_yes_count <- append(S_yes_count,
                      as.numeric(as.data.frame(table(market_sub_South[,i]))[which(as.data.frame(table(market_sub_South[,i]))$Var1=='y'),2]))
}

S_no_count <- c()
for(i in 29:54){
  S_no_count <- append(S_no_count,
                      as.numeric(as.data.frame(table(market_sub_South[,i]))[which(as.data.frame(table(market_sub_South[,i]))$Var1=='n'),2]))
}

S_column_name <- colnames(market_sub_South[,29:54])



S_T_3_1 <- cbind(as.data.frame(S_column_name),YorN='y',as.data.frame(S_yes_count))
colnames(S_T_3_1)[3] <- 'count'

S_T_3_2 <- cbind(as.data.frame(S_column_name),YorN='n',as.data.frame(S_no_count))
colnames(S_T_3_2)[3] <- 'count'

S_T_3 <- rbind(S_T_3_1,S_T_3_2)
S_T_3
```

```{r}
#market_sub_West 
W_yes_count <- c()
for(i in 29:54){
  W_yes_count <- append(W_yes_count,
                      as.numeric(as.data.frame(table(market_sub_West[,i]))[which(as.data.frame(table(market_sub_West[,i]))$Var1=='y'),2]))
}

W_no_count <- c()
for(i in 29:54){
  W_no_count <- append(W_no_count,
                      as.numeric(as.data.frame(table(market_sub_West[,i]))[which(as.data.frame(table(market_sub_West[,i]))$Var1=='n'),2]))
}

W_column_name <- colnames(market_sub_West[,29:54])



W_T_3_1 <- cbind(as.data.frame(W_column_name),YorN='y',as.data.frame(W_yes_count))
colnames(W_T_3_1)[3] <- 'count'

W_T_3_2 <- cbind(as.data.frame(W_column_name),YorN='n',as.data.frame(W_no_count))
colnames(W_T_3_2)[3] <- 'count'

W_T_3 <- rbind(W_T_3_1,W_T_3_2)
W_T_3
```


Build table (demo)
```{r demo}
yes_count <- c()
for(i in 29:54){
  yes_count <- append(yes_count,
                      as.numeric(as.data.frame(table(market[,i]))[which(as.data.frame(table(market[,i]))$Var1=='y'),2]))
}

no_count <- c()
for(i in 29:54){
  no_count <- append(no_count,
                      as.numeric(as.data.frame(table(market[,i]))[which(as.data.frame(table(market[,i]))$Var1=='n'),2]))
}

column_name <- colnames(market[,29:54])


T_3_1 <- cbind(item=as.data.frame(column_name),YorN='y',count=as.data.frame(yes_count))
colnames(T_3_1)[3] <- 'count'

T_3_2 <- cbind(item=as.data.frame(column_name),YorN='n',count=as.data.frame(no_count))
colnames(T_3_2)[3] <- 'count'

T_3 <- rbind(T_3_1,T_3_2)
T_3
```


Plot(demo)
```{r}
ggplot(T_3,aes(x = column_name ,y =count,fill=factor(YorN,levels=c("n","y" )),label=count))+
  geom_bar(stat="identity") +
  coord_flip()+
  xlab('Products')+
  ylab('Number of Farmers Market that have this product')+
  labs(fill = "YorN")+
  scale_fill_manual(values = c("orange1","olivedrab2"))+
  ggtitle("              Plot of Product Statistics")+
  theme(axis.text.y = element_text(color = "grey20", size = 10),
        axis.text.x = element_text(color = "grey20", size = 10),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold")
        )




```
Plot
```{r fig.height=8, fig.width=8}
#market_sub_Northeast 
P3_N <- ggplot(N_T_3,aes(x = N_column_name ,y =count,fill=factor(YorN,levels=c("n","y" )),label=count))+
  geom_bar(stat="identity") +
  coord_flip()+
  xlab('Products')+
  ylab('Number of Farmers Market that have this product')+
  labs(fill = "Have or Not")+
  scale_fill_manual(values = c("orange1","olivedrab2"))+
  ggtitle("Plot of Product Statistics \n(Farmers Market in Northeast US)")+
  theme(axis.text.y = element_text(color = "grey20", size = 10),
        axis.text.x = element_text(color = "grey20", size = 10),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold"),
        legend.position = "bottom"
        )+
  ylim(0, 2000)

#market_sub_Midwest
P3_M <- ggplot(M_T_3,aes(x = M_column_name ,y =count,fill=factor(YorN,levels=c("n","y" )),label=count))+
  geom_bar(stat="identity") +
  coord_flip()+
  xlab('Products')+
  ylab('Number of Farmers Market that have this product')+
  labs(fill = "Have or Not")+
  scale_fill_manual(values = c("orange1","olivedrab2"))+
  ggtitle("Plot of Product Statistics \n(Farmers Market in Midwest US)")+
  theme(axis.text.y = element_text(color = "grey20", size = 10),
        axis.text.x = element_text(color = "grey20", size = 10),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold"),
        legend.position = "bottom"
        )+
  ylim(0, 2000)

#market_sub_South
P3_S <- ggplot(S_T_3,aes(x = S_column_name ,y =count,fill=factor(YorN,levels=c("n","y" )),label=count))+
  geom_bar(stat="identity") +
  coord_flip()+
  xlab('Products')+
  ylab('Number of Farmers Market that have this product')+
  labs(fill = "Have or Not")+
  scale_fill_manual(values = c("orange1","olivedrab2"))+
  ggtitle("Plot of Product Statistics \n(Farmers Market in South US)")+
  theme(axis.text.y = element_text(color = "grey20", size = 10),
        axis.text.x = element_text(color = "grey20", size = 10),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold"),
        legend.position = "bottom"
        )+
  ylim(0, 2000)

#market_sub_West 
P3_W <- ggplot(W_T_3,aes(x = W_column_name ,y =count,fill=factor(YorN,levels=c("n","y" )),label=count))+
  geom_bar(stat="identity") +
  coord_flip()+
  xlab('Products')+
  ylab('Number of Farmers Market that have this product')+
  labs(fill = "Have or Not")+
  scale_fill_manual(values = c("orange1","olivedrab2"))+
  ggtitle("Plot of Product Statistics \n(Farmers Market in West US)")+
  theme(axis.text.y = element_text(color = "grey20", size = 10),
        axis.text.x = element_text(color = "grey20", size = 10),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold"),
        legend.position = "bottom")+
  ylim(0, 2000)

grid.arrange(P3_N, P3_M, P3_S, P3_W,ncol = 2)
```

# Problem 4
Give insights on payment modes used by the farmers market

```{r}
Pay_yes_count <- c()
for(i in 24:28){
  Pay_yes_count <- append(Pay_yes_count,
                      as.numeric(as.data.frame(table(market[,i]))[which(as.data.frame(table(market[,i]))$Var1=='y'),2]))
}

Pay_no_count <- c()
for(i in 24:28){
  Pay_no_count <- append(Pay_no_count,
                      as.numeric(as.data.frame(table(market[,i]))[which(as.data.frame(table(market[,i]))$Var1=='n'),2]))
}

Pay_column_name <- colnames(market[,24:28])



Pay_T_3_1 <- cbind(as.data.frame(Pay_column_name),YorN='y',as.data.frame(Pay_yes_count))
colnames(Pay_T_3_1)[3] <- 'count'

Pay_T_3_2 <- cbind(as.data.frame(Pay_column_name),YorN='n',as.data.frame(Pay_no_count))
colnames(Pay_T_3_2)[3] <- 'count'

Pay_T_3 <- rbind(Pay_T_3_1,Pay_T_3_2)
Pay_T_3

```

```{r}
ggplot(Pay_T_3,aes(x = Pay_column_name ,y =count,fill=factor(YorN,levels=c("n","y" )),label=count))+
  geom_bar(stat="identity") +
  coord_flip()+
  xlab('Products')+
  ylab('Number of Farmers Market that have this product')+
  labs(fill = "Have or Not")+
  scale_fill_manual(values = c("orange1","olivedrab2"))+
  ggtitle("Plot of Product Statistics \n(Farmers Market in West US)")+
  theme(axis.text.y = element_text(color = "grey20", size = 10),
        axis.text.x = element_text(color = "grey20", size = 10),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold"),
        legend.position = "bottom")


pct <- round(Pay_yes_count/sum(Pay_yes_count)*100)

Pay_column_name <- paste(Pay_column_name, pct) # add percents to labels 
Pay_column_name <- paste(Pay_column_name,"%",sep="") # ad % to labels 


pie(Pay_yes_count, labels = Pay_column_name, main="Pie Chart of Payment modes")
```


# Problem 5
Give insights that are derived from the combination of above four questions.
```{r}
#Northeast
market_sub_Multiple <- market[,c(3,13,35)]
market_sub_Multiple_1 <- subset(market_sub_Multiple,State %in% Northeast)
market_sub_Multiple_1$Area <- "Northeast"

dates_Multiple_1 <- c()
for( i in 1:nrow(market_sub_Multiple_1) ){
  dates_Multiple_1 <- append(dates_Multiple_1,as.Date(market_sub_Multiple_1[i,2], "%m/%d/%Y"))
}

Northeast_multiple <- cbind(market_sub_Multiple_1[,-2],as.data.frame(year(dates_Multiple_1)))
colnames(Northeast_multiple)[4] <- "year"
Northeast_multiple
```

```{r}
#Midwest
market_sub_Multiple_2 <- subset(market_sub_Multiple,State %in% Midwest)
market_sub_Multiple_2$Area <- "Midwest"

dates_Multiple_2 <- c()
for( i in 1:nrow(market_sub_Multiple_2) ){
  dates_Multiple_2 <- append(dates_Multiple_2,as.Date(market_sub_Multiple_2[i,2], "%m/%d/%Y"))
}

Midwest_multiple <- cbind(market_sub_Multiple_2[,-2],as.data.frame(year(dates_Multiple_2)))
colnames(Midwest_multiple)[4] <- "year"
Midwest_multiple
```

```{r}
#South
market_sub_Multiple_3 <- subset(market_sub_Multiple,State %in% South)
market_sub_Multiple_3$Area <- "South"

dates_Multiple_3 <- c()
for( i in 1:nrow(market_sub_Multiple_3) ){
  dates_Multiple_3 <- append(dates_Multiple_3,as.Date(market_sub_Multiple_3[i,2], "%m/%d/%Y"))
}

South_multiple <- cbind(market_sub_Multiple_3[,-2],as.data.frame(year(dates_Multiple_3)))
colnames(South_multiple)[4] <- "year"
South_multiple
```

```{r}
#West
market_sub_Multiple_4 <- subset(market_sub_Multiple,State %in% West)
market_sub_Multiple_4$Area <- "West"

dates_Multiple_4 <- c()
for( i in 1:nrow(market_sub_Multiple_4) ){
  dates_Multiple_4 <- append(dates_Multiple_4,as.Date(market_sub_Multiple_4[i,2], "%m/%d/%Y"))
}

West_multiple <- cbind(market_sub_Multiple_4[,-2],as.data.frame(year(dates_Multiple_4)))
colnames(West_multiple)[4] <- "year"
West_multiple

```

```{r}
multiple_bind <- rbind(Northeast_multiple,Midwest_multiple,South_multiple,West_multiple)
multiple_bind <- na.omit(multiple_bind)

for (k in 1:nrow(multiple_bind)) {
  if(multiple_bind$Seafood[k]=="y"){
    multiple_bind$seafood[k] <- 1
  }else{
    multiple_bind$seafood[k] <- 0
  }
}

multiple_bind <- multiple_bind[,-2]

multiple_summarise <- summarise(group_by(multiple_bind,Area,year),count_seafood=sum(seafood))
multiple_summarise

multiple_summarise <- subset(multiple_summarise,year %in% c(2012:2019))
```

```{r}
ggplot(multiple_summarise,aes(factor(year),count_seafood,fill=factor(Area)))+
  geom_bar(stat="identity",position="dodge")+
  scale_fill_manual(values = c("#44bec7","#ffc300","#fa3c4c","#d696bb"))+
  ggtitle("Number of Farmers Markets that Offers Seafood\nin Different Area from 2012 to 2019")+
  xlab("Year")+
  ylab("Number of Farmers Markets")+
  labs(fill="Area")+
  theme(axis.text.y = element_text(color = "grey20", size = 10),
        axis.text.x = element_text(color = "grey20", size = 10),
        axis.title.x = element_text(color = "grey20", size = 15),
        axis.title.y = element_text(color = "grey20", size = 15),
        plot.title = element_text(color="yellow4",size=20,face="bold"),
        legend.position = "bottom")
```

